### 2021-06-04 README.Rmd
New function (get_OSF_csv) to simplify getting data from OSF

```{r, results='hide', message=FALSE, warning=FALSE,echo=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(httr)
library(onsetsync)
```

```{r message=FALSE,warning=FALSE,eval=TRUE}
# Onsets
invisible(GET("https://osf.io/8a347/?action=download", 
              write_disk("CSS_Song2_Onsets_Selected.csv", overwrite = T)))
CSS_Song2_Onset<-read.csv("CSS_Song2_Onsets_Selected.csv",header=T,sep=",")
knitr::kable(head(CSS_Song2_Onset[,1:8,]),format = "simple",
             caption = 'Onset data structure (see text for details).')

# Annotations
invisible(GET("https://osf.io/4cdpr/?action=download", 
              write_disk("CSS_Song2_Metre.csv", overwrite = TRUE)))
CSS_Song2_Metre <- read.csv("CSS_Song2_Metre.csv", header=T, sep=",")
knitr::kable(head(CSS_Song2_Metre[1:4,]),format = ,"simple")
CSS_Song2_Onset <- dplyr::select(CSS_Song2_Onset,
                                 Label.SD,SD,Clave,Bass,Guitar,Tres) 
```

>>>>

```{r, message=FALSE, warning=FALSE,echo=TRUE}
library(onsetsync)
library(httr)
library(dplyr)
library(ggplot2)
```

```{r message=FALSE,warning=FALSE,eval=TRUE,results='asis'}
CSS_Song2_Onset <- get_OSF_csv('8a347') # Onsets
knitr::kable(head(CSS_Song2_Onset[,1:8,]),format = "simple",
             caption = 'Onset data structure (see text for details).')

CSS_Song2_Metre <- get_OSF_csv('4cdpr') # Annotations
knitr::kable(head(CSS_Song2_Metre[1:4,]),format = ,"simple")
CSS_Song2_Onset <- dplyr::select(CSS_Song2_Onset,
                                 Label.SD,SD,Clave,Bass,Guitar,Tres) 
```
